\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{setspace}

% Color scheme
\definecolor{primary}{HTML}{2c3e50}    % Dark blue for headings
\definecolor{secondary}{HTML}{3498db}  % Blue for accents
\definecolor{gray}{HTML}{7f8c8d}       % Gray for secondary text

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Уменьшил поля документа
\addtolength{\oddsidemargin}{-0.6in}   % Было -0.5in
\addtolength{\evensidemargin}{-0.6in}  % Было -0.5in
\addtolength{\textwidth}{1.2in}        % Было 1in
\addtolength{\topmargin}{-0.7in}       % Было -0.5in
\addtolength{\textheight}{1.2in}       % Было 1.0in

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large\color{primary}
}{}{0em}{}

%-------------------------
% Custom commands

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{\color{primary}#1}{: \color{black}#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\color{primary}#1} & \color{gray}#2 \\
      \textit{\small\color{gray}#3} & \textit{\small\color{gray} #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingSimple}[3]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\color{primary}#1} & \color{gray}#2 \\
      \textit{\small\color{gray}#3} & \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\color{secondary}\circ$}
\renewcommand{\labelitemi}{$\color{secondary}\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\link}[2]{\href{#1}{#2}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE\color{primary} Anton Kuznets} & \href{mailto:fgfgfb93@gmail.com}{fgfgfb93@gmail.com} \\
  & Telegram: \href{https://t.me/Astronomax}{@Astronomax} \\
  \link{https://github.com/Astronomax}{github.com/Astronomax} & \\
  \link{https://codeforces.com/profile/Astronomax}{codeforces.com/profile/Astronomax} & \\
\end{tabular*}

%-----------SUMMARY-----------
\vspace{2pt}
Interested in algorithms, data structures, databases, and performance optimization.

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Developer}{Aug. 2023 -- Present}
      {Tarantool DBMS (VK digital technologies)}{}
      \begin{itemize}
        \item Improvements in the replication system
        \item Improvements in MVCC
      \end{itemize}
  \resumeSubHeadingListEnd

%--------------EDUCATION--------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Computer Science}{Sep. 2024 -- Present}
      {Saint Petersburg State University}{}
    \resumeSubheading
      {Bachelor of Computer Science}{Sep. 2020 -- Jul. 2024}
      {Saint Petersburg State University}{}
    \resumeSubheadingSimple
      {Algorithmic Parallel A', Tinkoff Generation}{2019-2020}{}
    \resumeSubheadingSimple
      {Algorithmic Parallel B+, School of Olympiad Preparation, Innopolis University}{Jul 2019}{}
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\link{https://github.com/Astronomax/vrptw-powerful-route-minimization-heuristic}{VRPTW Route Minimization Heuristic}}
      {Implementation of heuristic algorithm for Vehicle Routing Problem with Time Windows. \textbf{C, C++}}

    \resumeSubItem{\link{https://github.com/Astronomax/blob-detection-and-tracking}{Blob Detection and Tracking Library}}
      {High-performance C++/Python computer vision library for blob detection and object tracking. \textbf{C++, Python}}

    \resumeSubItem{\link{https://github.com/Astronomax/compilers-supplementary}{Lama Compiler (Compiler Course Assignment)}}
      {Course assignment for a compilers course. Implements a compiler from the Lama language to both bytecode and assembler, along with a recursive stack machine bytecode interpreter both written in Lama. \textbf{Lama}}
    \resumeSubItem{\link{https://github.com/Astronomax/lamai}{Lama Bytecode Interpreter (VM Course Assignment)}}
      {Iterative interpreter for the educational Lama programming language stack machine bytecode. \textbf{C}}
    
    \resumeSubItem{\link{https://github.com/Astronomax/graphics-course-practice}{Computer Graphics Course Assignments}}
      {A collection of practical assignments completed for a university computer graphics course. Implements various core computer graphics algorithms and rendering techniques. \textbf{C++, GLSL}}

    \resumeSubItem{\link{https://github.com/Astronomax/raytracing-seminar-practice}{Ray Tracing Seminar Practice}}
      {A collection of practical assignments from a ray tracing seminar. Implements core ray tracing algorithms for rendering 3D scenes, including geometry intersection, lighting, and material simulation. \textbf{C++}}
  \resumeSubHeadingListEnd

\begin{comment}
%-----------COMPETITIVE PROGRAMMING-----------
\section{Competitive Programming}
  \resumeSubHeadingListStart
    \resumeSubheadingSimple
      {ICPC Northwestern Russia Regional Contest (1/4)}{2021}{12th place}
    \resumeSubheadingSimple
      {ITMO Olympiad in Informatics}{2020}{1st degree diploma}
    \resumeSubheadingSimple
      {Moscow Olympiad in Informatics}{2020}{2nd degree diploma}
    \resumeSubheadingSimple
      {SPbSU Olympiad in Informatics}{2020}{2nd degree diploma}
    \resumeSubheadingSimple
      {HSE Olympiad in Informatics}{2020}{2nd degree diploma}
  \resumeSubHeadingListEnd
\end{comment}

%--------PROGRAMMING LANGUAGES------------
\section{Languages}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ll}
  \textbf{Main:} C, C++ & \textbf{Familiar:} Go, Rust, Python, Kotlin, JavaScript, Haskell 
\end{tabular*}

%-------------------------------------------

\end{document}
